cardinalR: Generating interesting high-dimensional data structures

### 2025-11-07 paper-cardinalR.Rmd
Try to reduce the number of pages

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.", fig.width=12, fig.height=16, fig.pos="H"}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="100%", fig.align='center', fig.pos="H"}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `trefoil4d` (a1-a3) and $3\\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H"}

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.", fig.width=12, fig.height=16, out.width="100%", fig.align='center', fig.pos="H"}

>>>>

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.", fig.width=12, fig.height=16, fig.pos="H", out.width="80%", fig.align='center'}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="80%", fig.align='center', fig.pos="H"}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `trefoil4d` (a1-a3) and $3\\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H", out.width="80%", fig.align='center'}

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.", fig.width=12, fig.height=16, out.width="70%", fig.align='center', fig.pos="H"}

### 2025-11-07 paper-cardinalR.tex
Try to reduce the number of pages

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/pyr-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.}\label{fig:pyr-proj}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/sphere-proj-1}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/trefoil-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, `trefoil4d` (a1-a3) and $3\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.}\label{fig:trefoil-proj}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/triginometric-proj-1}

>>>>

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/pyr-proj-1}

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.}\label{fig:pyr-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/sphere-proj-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/trefoil-proj-1}

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, `trefoil4d` (a1-a3) and $3\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.}\label{fig:trefoil-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.7\linewidth]{paper-cardinalR_files/figure-latex/triginometric-proj-1}
